Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-03 tex/VHzQ.tex
VHzQ.pdf update

      \begin{tabular}{l r l}
        \hline  \hline
        Selection   & number detected (\%) \\
        \hline  
        Any band ($ZYJHK/K_{s}$   &  449  (97.0) \\
        $Z$-band    &  75  (16.1) \\
        $Y$-band    &  273  (59.0) \\
        $J$-band    &  447  (96.5) \\
        $H$-band    &  269  (58.1) \\
        $K$ or $Ks$-band    &  322  (69.5) \\
        \hline  \hline
      \end{tabular}
      \caption{Detection rate of VH$z$Qs in the near-infrared.}
      \label{tab:nir_detection}
    \end{table}

@@

\begin{figure}[H]
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
    \caption{MMTJ0215-0529}
    \label{fig:1}
  \end{subfigure}%
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
    \caption{CFHQSJ0216-0455}
    \label{fig:2}
  \end{subfigure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
    \caption{SHELLQsJ0220-04323}
    \label{fig:3}
  \end{subfigure}
  \medskip
\end{figure}

@@

>>>>

      \begin{tabular}{l r l}
        \hline  \hline
        Selection   & number detected (\%) \\
        \hline  
        Any band ($ZYJHK/K_{s}$   &  449  (97.0) \\
        $Z$-band    &  75  (16.2) \\
        $Y$-band    &  273  (59.0) \\
        $J$-band    &  447  (96.5) \\
        $H$-band    &  269  (58.1) \\
        $K$ or $Ks$-band    &  322  (69.5) \\
        \hline  \hline
      \end{tabular}
      \caption{Detection rate of VH$z$Qs in the near-infrared.}
      \label{tab:nir_detection}
    \end{table}

@@

\begin{figure}[H]
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
    \caption{MMTJ0215-0529}
    \label{fig:MMTJ0215-0529}
  \end{subfigure}%
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
    \caption{CFHQSJ0216-0455}
    \label{fig:CFHQSJ0216-0455}
  \end{subfigure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
    \caption{SHELLQsJ0220-0432}
    \label{fig:SHELLQsJ0220-0432}
  \end{subfigure}
  \medskip
\end{figure}

@@

VHS, Area 1: 150$<$RA/deg$<200$ annd $-40<$Decl./deg$<-20$:
$Y$=21.1 mag, $J$=20.6 mag, $H$=20.3 mag, $K_{s}$=19.8 mag (all AB). 
Area 2: 10$<$RA/deg$<$60, $-60<$Dec$<-40$:
$J$=21.2 mag, $H$=20.6 mag, $K_{s}$=20.2 mag.

VIKING is more uniform, so I calculated the averages over the whole area:
$Z$=22.7 mag, $Y$=21.9 mag, $J$=21.4 mag, $H$=21.2 mag, $Ks$=21.1 mag.

\begin{figure}[h]
  \centering
  \includegraphics[width=8.5cm]{../data/WSA_VSA/VHS_H_abMagLim.png}
  \caption{The calculated average {\tt AB MAGLIM} in the VHS.
    As one can see, VHS is not completely uniform. The are 3 areas with different filter sets, 
    and the depths changed in 2 of these areas, particularly in $J$ and $K_{s}$. 
    Y and H are almost uniform, but the coverage is much less.}
  \label{fig:1}
\end{figure}
